% prelude.tex
%   - titlepage
%   - dedication (optional)
%   - approval sheet
%   - course certificate
%   - table of contents, list of tables and list of figures
%   - nomenclature
%   - abstract
%============================================================================


\clearpage\pagenumbering{roman}  % This makes the page numbers Roman (i, ii, etc)


% TITLE PAGE
%   - define \title{} \author{} \date{}
\title{Design \& Implementation of Quantum Computing Immune Cryptography Processor}
%\author{Abhishek Agrawal \\ Souradip Pal}
\author{\hspace{-10mm}Abhishek Agrawal\hspace{8mm}Souradip Pal\\\hspace{-6mm}(150102002)\hspace{19mm}(150102076)}

%\authorone{Abhishek Agrawal}
%\authortwo{Souradip Pal}

\date{April 2019}

%  - Roll number, required for title page, approval sheet, and
%    certificate of course work
\rollnum{150102002\hspace{10mm}150102076}
%\rollnumone{150102002}
%\rollnumtwo{150102076}

%   - The default degree is ``Doctor of Philosophy''
%     (unless the document style msthesis is specified
%      and then the default degree is ``Master of Science'')
%     Degree can be changed using the command \iitbdegree{}
\iitgdegree{\textbf{Bachelor of Technology}}

%   - The default report type is preliminary report.
%      * for a PhD thesis, specify \thesis
\thesis
%      * for a M.Tech./M.Phil./M.Des./M.S. dissertation, specify \dissertation
%\dissertation
%      * for a DIIT/B.Tech./M.Sc.project report, specify \project
%\project
%      * for any other type, use  \reporttype{}
%\reporttype{project}

%   - The default department is ``Unknown Department''
%     The department can be changed using the command \department{}
\department{Department of Electronics \& Electrical Engineering}

%    - Set the guide's name
\setguide{Dr. Gaurav Trivedi}

%   - once the above are defined, use \maketitle to generate the titlepage
\maketitle

%--------------------------------------------------------------------%
% APPROVAL SHEET
%   - for final thesis, you need Approval Sheet. So, uncomment the
%     \makeapproval command.
%     it should come after dedication, if dedication is
%     present. Otherwise it is the first page after title page.
% \makeapproval


%--------------------------------------------------------------------%
% COPYRIGHT PAGE
%   - To include a copyright page use \copyrightpage
% \copyrightpage

%--------------------------------------------------------------------%

% ACKNOWLEDGMENTS (optional)
%\begin{acknowledgments}
%Sample Acknowledgement
%\end{acknowledgments}


% ABSTRACT
\begin{abstract}

Recent advancements in the domain of Quantum Computing are posing a security threat to most of the classical cryptographic methods and algorithms. Most popular symmetric and asymmetric cryptosystems including RSA, ECC, DES, Diffie-Hellman etc. can be efficiently broken down by a quantum computer running Shor's Algorithm. There exist two methods to counter this threat: firstly using \textbf{Quantum Cryptography} which involves setting up a quantum channel, quantum computers and would require a complete overhaul of the data communication infrastructure. Second alternative called \textbf{Post-Quantum Cryptography}, can however be implemented on the existing infrastructure and is equally resistant to classical and quantum crypto-attacks. Post-Quantum Cryptographic algorithms are more immune to these attacks because they are designed on the weakness of quantum circuits and algorithms. Hash, Code, Lattice based and Multivariate Polynomial based cryptographic algorithms are the most popular class of such algorithms. {\em In this report, we present the design and hardware implementation of a chaos-based post-quantum cryptographic system derived from a mechanical model showing non-linear dynamics and show its resistance against quantum computing attacks.} We also provide in this report the details of the encryption-decryption algorithms and experimentations performed on the implementation of the system in {\em Artix FPGA} hardware platform. 

\end{abstract}


%--------------------------------------------------------------------%
% CONTENTS, TABLES, FIGURES
\tableofcontents
%\listoftables
\listoffigures

%--------------------------------------------------------------------%
% NOMENCLATURE
\begin{nomenclature}
\begin{description}
\item{\makebox[0.75in][l]{{FPGA}}} Field Programmable Gate Array

\item{\makebox[0.75in][l]{{DSA}}} Digital Signature Algorithm

\item{\makebox[0.75in][l]{{RSA}}} Rivest-Shamir-Adleman

\item{\makebox[0.75in][l]{{DES}}} Data Encryption Standard

\item{\makebox[0.75in][l]{{PQC}}} Post-Quantum Cryptography

\item{\makebox[0.75in][l]{{ECC}}} Elliptic Curve Cryptography

\item{\makebox[0.75in][l]{{NTRU}}} Nth-Degree Truncated Polynomial Ring

\item{\makebox[0.75in][l]{{ODE}}} Ordinary Differential Equation

\item{\makebox[0.75in][l]{{CLB}}} Configurable Logic Block

\item{\makebox[0.75in][l]{{ALU}}} Arithmetic Logic Unit

\item{\makebox[0.75in][l]{{LUT}}} Look-Up Table

\item{\makebox[0.75in][l]{{USB}}} Universal Serial Bus

\item{\makebox[0.75in][l]{{FSM}}} Finte State Machine

\item{\makebox[0.75in][l]{{HDL}}} Hardware Description Language

\item{\makebox[0.75in][l]{{RTL}}} Resistor Transfer Level
\end{description}
\end{nomenclature}

\cleardoublepage\pagenumbering{arabic} % Make the page numbers Arabic (1, 2, etc)
